Gompertzian growth as infinitely correlated non-local growth

### 2023-08-07 arxiv2/new_draft.tex
small change

If we remove the dependency on time altogether, we observe the exponential growth equation
\begin{equation}
  \frac{d}{dt}\ln s(t) = - k,
\end{equation}
which yields 
\begin{equation}
  s(t) = A e^{ - k t}.
\end{equation}
This exponential equation implies a complete independence on both time and of the mutual entities involved in the growth. In the context of measurement error this function would be the Laplacian error which states that absolute measurement error decreases linearly with the error itself \footnote{Or as Laplace originally stated: ``[...] we have no reason to suppose a different law for the ordinates than for their differences'' \cite{stahl2006evolution}.}. Note also that for both the Gaussian and the exponential growth functions, the \textit{realized abundance}, $x(t)$, could be substituted as the dependent variable but then the physical interpretation would be a decay process.

As a side note, the Poisson distribution can be included in this discussion as the distribution which governs the infinitesimal growth rate of a coherent or infinitely correlated group of entities. By letting the growth rate be the rate at which a zero-count is observed, one recovers the Gompertz model where the Poisson mean parameter equals $\beta$ in Equation \ref{eq:Gomp}. This argument was put forth by \citet{shklovskii2005simple} although \citet{glauber1963coherent} was the first to point out the connection where the Poisson distribution reflects a coherent system. One the other hand, Glauber also showed that incoherent systems follow the Gaussian distribution. This mapping between coherence and incoherence was postulated as a medical diagnostic technique by \citet{zhang1994log}.

>>>>

If we remove the dependency on time altogether, we observe the exponential growth equation
\begin{equation}
  \frac{d}{dt}\ln s(t) = - k,
\end{equation}
which yields 
\begin{equation}
  s(t) = A e^{ - k t}.
\end{equation}
This exponential equation implies a complete independence on both time and of the mutual entities involved in the growth. In the context of measurement error this function would be the Laplacian error which states that absolute measurement error decreases linearly with the error itself \footnote{Or as Laplace originally stated: ``[...] we have no reason to suppose a different law for the ordinates than for their differences'' \cite{stahl2006evolution}.}. Note also that for both the Gaussian and the exponential growth functions, the \textit{realized abundance}, $x(t)$, could be substituted as the dependent variable where the physical interpretation would be a decay process.

As a side note, the Poisson distribution can be included in this discussion as the distribution which governs the infinitesimal growth rate of a coherent or infinitely correlated group of entities. By letting the growth rate be the rate at which a zero-count is observed with the Poisson mean parameter equal to $\beta t$, one recovers the Gompertz model in Equation \ref{eq:Gomp}. This argument was put forth by \citet{shklovskii2005simple} although \citet{glauber1963coherent} was the first to point out the connection where the Poisson distribution reflects a coherent system. One the other hand, Glauber also showed that incoherent systems follow the Gaussian distribution. This mapping between coherence and incoherence was postulated as a medical diagnostic technique by \citet{zhang1994log}.
